Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-07-11 paper-new/appendix.tex
edits to appendix

Before proceeding with the lemmas, we begin with a definition.

\begin{definition}[representation structure]\label{def:representation-structure}
  Let $A$ and $A'$ be value objects, and let $c : A \rel A'$ be a relation on
  the underlying predomains. A \emph{left-representation structure} $\rho^L_c$
  for $c$ consists of a predomain morphism $e_c : A \to A'$ such that $c$ is
  quasi-left-representable by $e_c$ (see Definition
  \ref{def:quasi-left-representable}). We similarly define a
  {right-representation structure} $\rho^R_c$ for $c$ to consist of a predomain
  morphism $p_c : A' \to A$ such that $c$ is quasi-right-representable by $p_c$
  (see Definition \ref{def:quasi-right-representable}).
  % (Notice that the direction of the morphism is opposite in the definition of
  % right-representation structure.)

  Likewise, let $d : B \rel B'$ be a computation relation. Left- and
  right-representation structures for $d$ are defined similarly, except the
  representing morphisms are now error domain morphisms rather than predomain
  morphisms.
\end{definition}

@@

>>>>

In this section we prove lemmas about quasi-representability needed for showing
that our notions of value and computation relation are compositional, and for
defining the action of the functors $U$, $\li$, $\arr$, and $\times$ on value
and computation relations.

@@

Next we show that the identity relation is quasi-representable.
